\documentclass[10pt]{article}

\title{Street Ministry \\
    \large Concentrating our Efforts }

% \author{Asher Mancinelli \\
%     Indian Trail Church \\
%     Spokane, WA 99218 \\
%     \texttt{ashermancinelli@gmail.com} }

\begin{document}
\maketitle
\section{Purpose}
    \begin{itemize}
        \item{We all represent churches in the Spokane area.}
        \item{We are all motivated by the gospel to serve the poor in our communities.}
        \item{We are all here to discuss how we may coordinate our efforts and build each other up.}
        \item{Specifically, how we may serve together this summer (June through August).}
    \end{itemize}
%/Purpose

\section{Scripture}
    We will meditate on the following Scripture before discussing the talking points. \\
    Deuteronomy 15:7-11 ---
    \begin{center}
        \textit{“If among you, one of your brothers should become poor, in any of your towns within your land that the Lord your God is giving you, you shall not harden your heart or shut your hand against your poor brother, but you shall open your hand to him and lend him sufficient for his need, whatever it may be. Take care lest there be an unworthy thought in your heart and you say, ‘The seventh year, the year of release is near,’ and your eye look grudgingly on your poor brother, and you give him nothing, and he cry to the Lord against you, and you be guilty of sin. You shall give to him freely, and your heart shall not be grudging when you give to him, because for this the Lord your God will bless you in all your work and in all that you undertake. For there will never cease to be poor in the land. Therefore I command you, ‘You shall open wide your hand to your brother, to the needy and to the poor, in your land.’}\footnote{English Standard Version}
    \end{center}
%/Scriptures

\clearpage

\section{Talking Points}
    We will limit each point to about 10-15 minutes, however all are free to continue the discussion afterwards.
    \begin{enumerate}
        \item{Current schedule/ministry plans for this summer (Kathy Lee)}
        \item{Teams for prep, delivery}
        \item{Finances}
            \begin{itemize}\item{about \$1/lunch}\end{itemize}
        \item{Union Gospel Mission Covenant}
    \end{enumerate}
%/Talking Points

\end{document}
