
\section{Opportunities to Equip the Saints}

    % I really want to convey here that there are issues in the church at the moment.
    % I want to be clear that there are some areas that I think we can and should grow in, what I think success looks like, and how I believe God is leading us there.
    % Problem -> Goal -> How we get there
    % In this pattern, I do not quite know how to organize the first section...
    % This section is especially open to reconstruction and correction
    In my experience with local churches, organizations and individuals in Spokane, believers tend to feel ill-equipped in several areas.
    Believers in middle- to upper-class Spokane tend to be somewhat removed from the needs of the poor.
    As a result, they do not know what physical needs they are able to meet, or what of those needs are of the highest priority.
    Believers rarely feel comfortable sharing the Gospel, which is significant because of the opportunities to share the gospel downtown.
    The church can bridge this gap by equipping:
    \editonlyfn{Editors: I intend to show (1) where the church is lacking, (2) what success looks like for the church, and (3) how we get from (1) to (2).
    In trying to convey this message, (1) always feels problematic.
    I am not sure how best to articulate the current shortcomings of the church in the service to the poor, so this section is especially open to recommendation.}
    \begin{enumerate}
        \item Team members to share the Gospel and pray with people
          \footnote{``\textit{Go therefore and make disciples of all nations, baptizing them in the name of the Father and of the Son and of the Holy Spirit, teaching them to observe all that I have commanded you.}'', Matthew 28:19-20}
        \item Members with information needed to tend to the physical needs of the poor
          \footnote{``\textit{If a brother or sister is poorly clothed and lacking in daily food, and one of you says to them, “Go in peace, be warmed and filled,” without giving them the things needed for the body, what good is that?}'', James 2:15-16}
        \item Leaders to coordinate and empower team members
          \footnote{``\textit{[W]hoever would be great among you must be your servant, and whoever would be first among you must be your slave, even as the Son of Man came not to be served but to serve, and to give his life as a ransom for many}'', Matthew 20:26-28}
    \end{enumerate}
    This is the standard laid out by Scripture, and should the Church be anything less than this, She is falling short of Her calling.
    \editonlyfn{Editors: this sentence was added to clarify that the Church seems to be failing in these areas in some capacity---to give it some teeth, where before the list was all phrased as positives (e.g. ``this is where we can grow'')}

\qJamesOneTwentySeven
