
\newcommand{\epigraphIT}[1]{
    \epigraph{\textit{#1}}
}

\newcommand{\editonlyfn}[1]{
    \ifdefined\isedit
    \footnote{#1}
    \fi
}

\def \qFirstCorTwelveTwentyEight {\epigraphIT{And God has appointed in the church first apostles, second prophets, third teachers, then miracles, then gifts of healing, helping, administrating, and various kinds of tongues.}{1 Corinthians 12:28}}

\def \qJamesOneTwentySeven {\epigraphIT{Religion that is pure and undefiled before God the Father is this: to visit orphans and widows in their affliction, and to keep oneself unstained from the world.}{{James 1:27}}}

\def \qJamesTwoFive {\epigraphIT{Listen, my beloved brothers, has not God chosen those who are poor in the world to be rich in faith and heirs of the kingdom, which he has promised to those who love him?}{{James 2:5}}}

\def \qGreatCommission {\epigraphIT{Go therefore and make disciples of all nations, baptizing them in the name of the Father and of the Son and of the Holy Spirit, teaching them to observe all that I have commanded you.}{{Matthew 28:19}}}

\def \qPiperCoronary {\epigraphIT{[Adrenaline] doesn't do much for Mondays. I am more thankful for my heart. It just keeps on serving\dots Coronary Christians are like the heart in the causes they serve\dots O, for coronary Christians! Christians committed to great Causes, not great comforts.}{John Piper\cite{coronary}}}

\def \qLeastOfThese {\epigraphIT{Truly I tell you, whatever you did for one of the least of these brothers and sisters of mine, you did for me.}{{Matthew 25:40}}}

\def \qJamesPhysical {\epigraphIT{If one of you says to them, “Go in peace; keep warm and well fed,” but does nothing about their physical needs, what good is it?}{{James 2:16}}}

\def \qTwoOrMoreAreGathered {\epigraphIT{For where two or three are gathered in my name, there am I among them.}{{Matthew 18:20}}}

\def \qLeaders {\epigraphIT{Let the greatest among you become as the youngest, and the leader as one who serves.}{{Luke 22:25-26}}}

\def \qChristianHedonism {\epigraphIT{God is most glorified in us when we are most satisfied in him\dots our pursuit of joy in him is essential.}{John Piper\cite{piper_1995}}}

\def \qHebSix {\epigraphIT{For God is not unjust so as to overlook your work and the love that you have shown for His name in serving the saints, as you still do.}{{Hebrews 6:10}}}

\def \qFirstThesFive {\epigraphIT{Now may the God of peace himself sanctify you completely, and may your whole spirit and soul and body be kept blameless at the coming of our Lord Jesus Christ.}{{1 Thessalonians 5:23}}}

\def \qJohnEdwardsJoy {\epigraphIT{God made the world that He might communicate, and the creature receive, His glory; and that it might [be] received both by the mind and heart.}{Jonathan Edwards\cite{taylor_piper_2004}}}

\def \qMattJesusSumm {}

\def \qGalaiansForgetPoor {}
